---
title: "COVID-19 Overview Shinydashboard"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{COVID-19 Overview Shinydashboard}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(covid19shiny)
```

This vignette is intended for the usage of `covid19shiny` package. It explains how to run the shiny application which illustrates the overview of COVID-19 state in the world and describes the functions contained inside the package. 

The package uses data sourced from `tidycovid19` package by Joachim Gassen by using the `download_merged_data` function. Alongside with that, `countries.csv` file taken from Google Developers and Shapefile taken from thematicmapping.org are used. 

Functions inside the package include:

## Installing the package
Before using the package, it must firstly be installed from [GitHub](https://github.com/etc5523-2020/r-package-assessment-helenevangelinaa).

```{r installing-pkg, eval=FALSE}
# install.packages("devtools")
devtools::install_github("etc5523-2020/r-package-assessment-helenevangelinaa")
```

## Running the application

After loading `library(covid19shiny)`, the shiny application could be launched by using the following code:
```{r launching-app, eval = FALSE}
launch_app()
```

## Example